Template Master's Thesis

### 2023-08-22 paper.tex
Update conclusion topics

The goal of this thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023.

All blockchain transaction and token transfer data is publicly available. This allows us to apply various heuristics to cluster addresses belonging to the same entity by exploiting activity patterns.

By focusing on Ethereum and Polygon on-chain data, we narrowed the address set down to 137,544.

We found .... to be applicable to cluster a predefined address set. The approaches had to be modified and extended.

Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
Best -> graph representation learning
Combination as extension
Approach, especially our node embedding implementation can be used and extended to cluster other predefined address set

1. Public blockchain -> all data available -> allows us to analyse it and find information
2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
3. Most successful graph representation learning because does not require participation in specific on-chain event / usage pattern, sehr vielversprechend
4. From the various methods Role2Vec best
5. Summarize Final results
6. For researchers -> extend this approach -> apply it to other address sets -> add activity patterns ->
7. Sth about bots

8. Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper, exciting to analyze other things, endless possibilities.
Address clustering will  make further advancements. From a user perspective it is important that privacy enhancing protocols are also further developed and users educated how to preserve privacy when transacting on blockchains. / in the context of blockchains

>>>>

The goal of this thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023. \newline
By exploiting activity patterns within the publicly available on-chain data, we are apble to apply various heuristics for clustering addresses controlled by the same entity. Focusing on Ethereum and Polygon on-chain data, we narrowed the address set down to 137,544.
After introducing various concepts needed to understand this complex topic, we efficiently collected the required on-chain data. This feat was achieved by using information if an address was active on Ethereum and Polygon and subsequently gathering all transactions and token transfers related to the addresses via Etherscan.

ENS pairs ...

We looked at the existing clustering heuristics and discussed their applicablilty to our research question/setting.
We found thee clustering heuristics, namely self-authorization, graph representation learning and non-compensated LAND transfers to be applicable to cluster a predefined address set. Self-authorization and graph representation learning through Ethereum transaction data were approaches proposed by \cite{FV:17} and \cite{Beres2020} respectively, while the LAND transfer heuristic was proposed by ourselves. We modified and extended the learned graph representation approach to best work with our research goal. As of our best knowledge, we are the first to work with intra-set asset transfers to construct the network graph for graph-representation learning.\newline 
The most successful clustering heuristic was graph representation learning, the reason being its general applicability, as it does not require participation in specific on-chain event / usage pattern. Topic for future research ... \newline
The node embedding approach could be possibly further extended by incorporating time-of-day activity or gas price selection patterns for better clustering performance of predefined address sets. \newline
Specifically looking at node embedding algorithms, we found the Role2Vec algorithm to be the most effective, finding the ground truth pair within the five nearest neighbors in 71 percent.

Results/ Evaluation ...

Clustering based on distance threshold, clusters dependent on this threshold...

Visualizations ...

Sth about bots ...

Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper, exciting to analyze other things, endless possibilities.
Address clustering will  make further advancements. From a user perspective it is important that privacy enhancing protocols are also further developed and users educated how to preserve privacy when transacting on blockchains. / in the context of blockchains

%1. Public blockchain -> all data available -> allows us to analyse it and find information
%2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
%3. sehr vielversprechend
%4. From the various methods Role2Vec best
%5. Summarize Final results
%6. For researchers -> extend this approach -> apply it to other address sets -> add activity patterns ->
%7. Sth about bots

%Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
%All blockchain transaction and token transfer data is publicly available. This allows us to apply various heuristics to cluster addresses belonging to the same entity by exploiting activity patterns.
